Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-28 README.Rmd
removed item from to do list

- Move all code and results from our work identifying the data to my LIME-research-journals repo for future reference (including LIME explanations from different training datasets/models)
- Rewrite Sections 4 and 5 as needed
- Prepare for submission
- Edit dataset descriptions in README and add to the readme.txt document for submission
- Upload the files for submission and submit

>>>>

- Move all code and results from our work identifying the data to my LIME-research-journals repo for future reference (including LIME explanations from different training datasets/models)
- Rewrite Sections 4 and 5 as needed
- Prepare for submission
- Upload the files for submission and submit
